Practical Hilbert space approximate Bayesian Gaussian processes for probabilistic programming

### 2020-06-17 Paper/manuscript_v2/manuscript_07_02.tex

The results from the previous section can be generalized to a multidimensional input space with compact support, $\Omega=[-L_1,L_1] \times \dots \times [-L_d,L_d]$ and Dirichlet boundary conditions. 
In a $D$-dimensional input space, the total number of eigenfunctions and eigenvalues in the approximation is equal to the number of $D$-tuples, that is, possible combinations of univariate eigenfunctions over all dimensions. The number of $D$-tuples is given by 
%
\begin{align} \label{eq_m_multi}
m^{\ast} = \prod_{d=1}^{D} m_d,
\end{align}
%
where $m_d$ is the number of basis function for the dimension $d$. Let $\mathbb{S}\in {\rm I\!N}^{m^{\ast} \times D}$ be the matrix of all those $D$-tuples. For example, suppose we have $D=3$ dimensions and use $m_{1}=2$, $m_{2}=2$ and $m_{3}=3$ eigenfunctions and eigenvalues for the first, second and third dimension, respectively. Then, the number of multivariate eigenfunctions and eigenvalues is $m^{\ast} = m_{1} \cdot m_{2} \cdot m_{3} = 12$ and the matrix $\mathbb{S}\in {\rm I\!N}^{12 \times 3}$ is given by
%
\begin{align}\small
\mathbb{S}=
\left[ {\begin{array}{ccc}
1 & 1 & 1 \nonumber \\
1 & 1 & 2 \\
1 & 1 & 3 \\
1 & 2 & 1 \\
1 & 2 & 2 \\
1 & 2 & 3 \\
2 & 1 & 1 \\
2 & 1 & 2 \\
2 & 1 & 3 \\
2 & 2 & 1 \\
2 & 2 & 2 \\
2 & 2 & 3 
\end{array} } \right].
\end{align}

>>>>

The results from the previous section can be generalized to a multidimensional input space with compact support, $\Omega=[-L_1,L_1] \times \dots \times [-L_D,L_D]$ and Dirichlet boundary conditions. 
In a $D$-dimensional input space, the total number of eigenfunctions and eigenvalues in the approximation is equal to the number of $D$-tuples, that is, possible combinations of univariate eigenfunctions over all dimensions. The number of $D$-tuples is given by 
%
\begin{align} \label{eq_m_multi}
m^{\ast} = \prod_{d=1}^{D} m_d,
\end{align}
%
where $m_d$ is the number of basis function for the dimension $d$. Let $\mathbb{S}\in {\rm I\!N}^{m^{\ast} \times D}$ be the matrix of all those $D$-tuples. For example, suppose we have $D=3$ dimensions and use $m_{1}=2$, $m_{2}=2$ and $m_{3}=3$ eigenfunctions and eigenvalues for the first, second and third dimension, respectively. Then, the number of multivariate eigenfunctions and eigenvalues is $m^{\ast} = m_{1} \cdot m_{2} \cdot m_{3} = 12$ and the matrix $\mathbb{S}\in {\rm I\!N}^{12 \times 3}$ is given by
%
\begin{align}\small
\mathbb{S}=
\left[ {\begin{array}{ccc}
1 & 1 & 1 \nonumber \\
1 & 1 & 2 \\
1 & 1 & 3 \\
1 & 2 & 1 \\
1 & 2 & 2 \\
1 & 2 & 3 \\
2 & 1 & 1 \\
2 & 1 & 2 \\
2 & 1 & 3 \\
2 & 2 & 1 \\
2 & 2 & 2 \\
2 & 2 & 3 
\end{array} } \right].
\end{align}
